On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-12-06 paper.tex
Changed abstract

\begin{abstract}
The relationship between the length of a line segment and the number of tiles it visits on a rectangular grid is addressed in this paper. For a segment with deterministic but arbitrary position and orientation, the maximum number of visited tiles given its length and the infimum length for a desired number of visited tiles are characterized. For a segment with random position and orientation, the average number of visited tiles and the probability of visiting the maximum number of tiles are studied. These questions are related to Buffon's needle problem and its extension by Laplace.

@@

\emph{MSC2020:} 52C99, 60D05. % ***Alex: check if there's a better one
% 52C99: Discrete geometry: None of the above, but in this section
% 60D05: Geometric probability and stochastic geometry
\end{abstract}

>>>>

\begin{abstract} % ***Alex: please check / revise 
The relationship between the length of a line segment and the number of tiles it visits on a rectangular grid is addressed in this paper. The square grid is also considered explicitly, as some of the specific problems studied are more tractable in that particular case. The segment position and orientation are modelled as either deterministic or random. In the former setting, the maximum number of visited tiles given the segment length and the infimum length for a desired number of visited tiles are characterized. For a segment of fixed length with random position and orientation, the average number of visited tiles and the probability of visiting the maximum number of tiles on a square grid are studied. These questions are related to Buffon's needle problem and its extension by Laplace.

@@

\emph{MSC2020:} 52C99, 60D05. % ***Alex: is there a better one?
% 52C99: Discrete geometry: None of the above, but in this section
% 60D05: Geometric probability and stochastic geometry
\end{abstract}
